The \dealii Library, Version 9.7

### 2025-08-20 9.7/paper.tex
Add author and funding

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Wolfgang Bangerth,
    Bruno Blais,
    Marc Fehling,
    Rene Gassm\"{o}ller,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Matthias Maier,
    Peter Munch,
    Bruno Turcksin,
    David Wells,
    Michał Wichrowski,
  },
  pdftitle={The deal.II Library, Version 9.7, 2025},
}

@@

\author[4]{Bruno Blais}
\affil[4]{Chemical Engineering High-performance Analysis, Optimization and Simulation (CHAOS) laboratory, Department of Chemical Engineering,
             Polytechnique Montréal,
             PO Box 6079, Stn Centre-Ville, Montréal, Québec, Canada, H3C 3A7.
             {\texttt{bruno.blais@polymtl.ca}}}

\author[5]{Marc~Fehling}
 \affil[5]{Department of Mathematical Analysis,
    Faculty of Mathematics and Physics, Charles University,
    Sokolovsk{\'a} 49/83, 186\,75 Prague 8, Czech Republic.
    {\texttt{marc.fehling@matfyz.cuni.cz}}}

\author[6]{Rene~Gassm\"{o}ller}
\affil[6]{GEOMAR Helmholtz Centre for Ocean Research Kiel, 24148 Kiel, Germany}

\author[7]{Timo~Heister}
 \affil[7]{School of Mathematical and Statistical Sciences,
   Clemson University,
   Clemson, SC, 29634, USA.
   {\texttt{heister@clemson.edu}}}

\author[8]{Luca~Heltai}
\affil[8]{Department of Mathematics, University of Pisa,
Via Buonarroti 1/c, 56127 Pisa, Italy.}

 \author[9]{Martin~Kronbichler}
 \affil[9]{Faculty of Mathematics, Ruhr University Bochum,
   Universit\"atsstr.~150, 44780 Bochum, Germany.
 {\texttt{martin.kronbichler@rub.de}}}

\author[10]{Matthias~Maier}
\affil[10]{Department of Mathematics,
  Texas A\&M University,
  3368 TAMU,
  College Station, TX 77845, USA.
  {\texttt{maier@math.tamu.edu}}}

\author[11]{Peter Munch}
 \affil[11]{Institute of Mathematics, Technical University of Berlin, Germany.
  {\texttt{muench@math.tu-berlin.de}}}

@@

\author[12]{Siarhei Uzunbajakau}
\affil[12]{CEM Books,
  Rotterdam, The Netherlands.
  {\texttt{info@cembooks.nl}}}

\author[13]{David Wells}
\affil[13]{Department of Mathematics, University of North Carolina,
  Chapel Hill, NC 27516, USA.
  {\texttt{drwells@email.unc.edu}}}

  \author[14]{Michał Wichrowski}
\affil[14]{Interdisciplinary Center for Scientific Computing, Heidelberg University, Heidelberg, Germany.
  {\texttt{mt.wichrowsk@uw.edu.pl}}}

@@

>>>>

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Wolfgang Bangerth,
    Maximilian Bergbauer,
    Bruno Blais,
    Marc Fehling,
    Rene Gassm\"{o}ller,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Matthias Maier,
    Peter Munch,
    Bruno Turcksin,
    David Wells,
    Michał Wichrowski,
  },
  pdftitle={The deal.II Library, Version 9.7, 2025},
}

@@

\author[4]{Maximilian~Bergbauer}
\affil[4]{Institute for Computational Mechanics, Technical University of
  Munich, Boltzmannstr. 15, 85748 Garching bei München, Germany.
  {\texttt{maximilian.bergbauer@tum.de}}}

\author[5]{Bruno Blais}
\affil[5]{Chemical Engineering High-performance Analysis, Optimization and Simulation (CHAOS) laboratory, Department of Chemical Engineering,
             Polytechnique Montréal,
             PO Box 6079, Stn Centre-Ville, Montréal, Québec, Canada, H3C 3A7.
             {\texttt{bruno.blais@polymtl.ca}}}

\author[6]{Marc~Fehling}
\affil[6]{Department of Mathematical Analysis,
    Faculty of Mathematics and Physics, Charles University,
    Sokolovsk{\'a} 49/83, 186\,75 Prague 8, Czech Republic.
    {\texttt{marc.fehling@matfyz.cuni.cz}}}

\author[7]{Rene~Gassm\"{o}ller}
\affil[7]{GEOMAR Helmholtz Centre for Ocean Research Kiel, 24148 Kiel, Germany}

\author[8]{Timo~Heister}
\affil[8]{School of Mathematical and Statistical Sciences,
   Clemson University,
   Clemson, SC, 29634, USA.
   {\texttt{heister@clemson.edu}}}

\author[9]{Luca~Heltai}
\affil[9]{Department of Mathematics, University of Pisa,
Via Buonarroti 1/c, 56127 Pisa, Italy.}

\author[10]{Martin~Kronbichler}
\affil[10]{Faculty of Mathematics, Ruhr University Bochum,
   Universit\"atsstr.~150, 44780 Bochum, Germany.
 {\texttt{martin.kronbichler@rub.de}}}

\author[11]{Matthias~Maier}
\affil[11]{Department of Mathematics,
  Texas A\&M University,
  3368 TAMU,
  College Station, TX 77845, USA.
  {\texttt{maier@math.tamu.edu}}}

\author[12]{Peter Munch}
\affil[12]{Institute of Mathematics, Technical University of Berlin, Germany.
  {\texttt{muench@math.tu-berlin.de}}}

@@

\author[13]{Siarhei Uzunbajakau}
\affil[13]{CEM Books,
  Rotterdam, The Netherlands.
  {\texttt{info@cembooks.nl}}}

\author[14]{David Wells}
\affil[14]{Department of Mathematics, University of North Carolina,
  Chapel Hill, NC 27516, USA.
  {\texttt{drwells@email.unc.edu}}}

\author[15]{Michał Wichrowski}
\affil[15]{Interdisciplinary Center for Scientific Computing, Heidelberg University, Heidelberg, Germany.
  {\texttt{mt.wichrowsk@uw.edu.pl}}}

@@

M.~Bergbauer was supported by the German Research Foundation (DFG) under the
project ``High-Performance Cut Discontinuous Galerkin Methods for Flow
Problems and Surface-Coupled Multiphysics Problems'' Grant Agreement
No.~456365667.
